Integer Programming Formulations for the Shared Multicast Tree Problem

### 2018-09-11 smt/response.tex

\documentclass[12pt]{article}
\usepackage{a4wide,url}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{color}

\begin{document}
\section*{Response Letter}
We are grateful to the reviewers for their time, effort, and constructive remarks.
All remarks have been accounted for in the revised version, as detailed in our response below.

\section*{Reviewer 2}
Our response in \textcolor{blue}{blue} follows the corresponding remark from the reviewer in \textcolor{red}{red}.

\begin{itemize}
\item \textcolor{red}{The abstract should be shorter.} \textcolor{blue}{
We have revised the abstract, and reduced its length from 22 to 15 lines.
}
\item \textcolor{red}{The literature review has not been organized in a proper format. The references are so old. New related works need to be explained. The authors should use a separate Section for this purpose and compare the novelty of the present approach with them.} \textcolor{blue}{
Following the recommendation of the reviewer, we have reorganized the literature review, and devoted a new section (Section 2 in the revised manuscript)
to this topic. We have also included a review of recent and relevant literature (references ??? in the revision).
In paragraph ??? of Section 2, we now state explicitly the contributions from the present work, and explain how they relate to the current literature.
}
\item \textcolor{red}{They also should consider a separate section on the network model and assumptions.} \textcolor{blue}{
We have restructured the former Section 2 (now Section 3) into three subsections.
The first is devoted to mathematical notation and underlying assumptions, the second addresses the network model,
while the problem definition is given in the third subsection.
}
\item \textcolor{red}{The diagrams of figures are not distinguishable in black and white print. The legends should be corrected.} \textcolor{blue}{
While paying particular attention to their appearance in black and white print, we have given all figures,
including their legends, a complete overhaul.
}
\item \textcolor{red}{All equations should be terminated with "." or "," as well as sentences.} \textcolor{blue}{
Done.
}
\item \textcolor{red}{The legends, markers and other details of the figures are so small.} \textcolor{blue}{
Legends, markers, and other details are now given in larger size.
}
\item \textcolor{red}{A fundamental weak point is that there are no numerical results comparing the proposed scheme with the other new works;} \textcolor{blue}{
We agree that a comparison with alternative contemporary methods largely benefits the paper.
To that end, we have included a comparison with ??? \cite{???}.
Results from the experiments are documented in the new Section 7.?
}
\item \textcolor{red}{The simulation graphs need more expiation and justification.} \textcolor{blue}{
For better justification of the numerical results illustrated graphically in the former Section 6 (now Section 7),
we have added more explanations in the caption of Fig. 3.
}
\item \textcolor{red}{ The main aim of this paper is the energy, How is the energy issue modeled? Why is not the real models used in the paper?} \textcolor{blue}{
In the new Section 3.2 on the network model, we now explain more detailed how the energy is modeled.
At the end of the section, we also describe how our model differs from another models in the literature.
Justification is added in terms of references to relevant and frequently cited works mentioned in Section 2 (see Wieselthier et al. (2000), Das et al. (2003), Altinkemer et al. (2005),
Yuan (2005), Yuan et al. (2008), Bauer et al. (2008), Montemanni and Leggieri (2011) and Leggieri et al. (2008), etc.).
}
\item \textcolor{red}{Overall the novelty of the proposed approach in unclear and the paper is hard to follow
The authors have not considers the wireless problems in the paper.} \textcolor{blue}{
The novelty of and the contributions from the paper are now explicitly stated in Section 2.
We also explain how the paper relates to other works on energy minimization in wireless networks.
}
\end{itemize}

### 2018-09-11 smt/sec6-exp.tex
MI (SMT): Addressed the criticism of Reviewer 2 and added more explanation to the graphs in Fig. 3. Also updated the response letter accordingly.

We compare the progress of the lower bounds obtained by the CG method with the one obtained by B\&B applied to $\mathcal{F}_1$.
 as a function of running time.
Instances with $|V|=2|D|\in\{24, 26,\ldots, 34\}$ are investigated, with 5 instances for each value of $|V|$.
The results are illustrated in Fig. \ref{fig:cggr}.
Each curve represents the progress of the lower bound within each instance set.
The horizontal axes represent running times ranging from 0 to 20 CPU-minutes.
The vertical axes correspond to the lower bounds as a percentage of $z\left(\text{LP}(\mathcal{F}_1)\right)$, averaged over all instances in the set.

@@

    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{lower-bound-32-16}
        \caption{$|V|=32, |D|=16$}
        \label{fig:cggr32-16}
    \end{subfigure}
    \hfill %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{lower-bound-34-17}
        \caption{$|V|=34, |D|=17$}
        \label{fig:cggr34-17}
    \end{subfigure}
  \caption{Comparison of lower bounds obtained by CG and B\&B on model $\mathcal{F}_1$. }
  \label{fig:cggr}
\end{figure}

>>>>

We compare the progress of the lower bounds obtained by the CG method with the one obtained by B\&B applied to $\mathcal{F}_1$ as a function of running time.
Instances with $|V|=2|D|\in\{24, 26,\ldots, 34\}$ are investigated, with 5 instances for each value of $|V|$.
The results are illustrated in Fig. \ref{fig:cggr}.
Each curve represents the progress of the lower bound within each instance set.
The horizontal axes represent running times ranging from 0 to 20 CPU-minutes.
The vertical axes correspond to the lower bounds as a percentage of $z\left(\text{LP}(\mathcal{F}_1)\right)$, averaged over all instances in the set.

@@

    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{lower-bound-32-16}
        \caption{$|V|=32, |D|=16$}
        \label{fig:cggr32-16}
    \end{subfigure}
    \hfill %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{lower-bound-34-17}
        \caption{$|V|=34, |D|=17$}
        \label{fig:cggr34-17}
    \end{subfigure}
  \caption{Comparison of lower bounds obtained by CG and B\&B on model $\mathcal{F}_1$.
	\textcolor{blue}{Each figure depicts a progress of lower bounds for instances with varying number of destination and non-destination nodes.
	The lower bounds are obtained by solving CG scheme applied on model $\mathcal{F}_1$ (black curves), and produced during the course of classic B\&B algorithm (grey curves)
	The tightness of the bounds increases with time, and it can be observed from the graphs that the CG bound becomes tighter at some point.
	We express the quality of lower bounds with respect to the value of simple continuous relaxatin, as indicated by the vertical axes.
	It can also be noted that the lower bound obtained from B\&B grows sharply during the computation of the simplex method in the root of the B\&B tree, 
	which is happening until the curve reaches 100\%.
	After that point the bound grows rather slowly.
	CG on the other hand produces bound that grows faster even after the value of first relaxation in the root is reached.
	}}
  \label{fig:cggr}
\end{figure}
